%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  v1: RSC 9/28-29
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%\documentclass[12pt]{article}
\documentclass[11pt]{article}
\usepackage{epsf}
%\usepackage{times}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{tabularx}
\usepackage{multirow}
%\usepackage{mathptm}
 
%\textwidth 6.7in
\textwidth 6.43in
\textheight 9.in
\topmargin -0.5truein
\oddsidemargin 0mm
\evensidemargin 0mm
\raggedbottom
%\pagestyle{headings}

\begin{document}

\pagenumbering{arabic}

\noindent
{\Large \bf Postdoctoral Mentoring Plan}
\bigskip

One postdoctoral researcher will be funded on this project. The
postdoctoral researcher's development will be monitored and enhanced through a program of structured
mentoring activities. The  goal of the mentoring program will be to
provide the skills, knowledge and experience to prepare the postdoctoral
researcher to excel in his/her career path. To accomplish this goal, the
mentoring plan will provide career planning assistance and opportunities
to learn a number of career skills such as writing grant proposals,
advising and teaching students, writing articles for publication, and last but not least 
communication skills. Specific elements of the mentoring plan will include:

\begin{itemize}

\item Individual consultations on how to identify research funding
  opportunities and write competitive proposals.

\item Participation in seminars and workshops on teaching and learning.

\item Opportunities to network with visiting scholars who are leaders in
  our field by having lunch or dinner with them when they participate in
  the department's visiting speaker series.

\item Participation in a joint journal club with the High Energy Physics
  Group at the University of Rochester where students, postdocs and
  faculty members meet, discuss and critique recent journal articles in
  the field.

\item Participation in the {\sl ``Postdoc Survival Skills Workshops''} offered by the UB
 Office of Postdoctoral Scholars. 

\item Travel to several conferences and/or workshops each year (travel
  funds are included in the budget), with the goal that the postdoctoral
  fellow presents his/her research work at the conference or workshop.

\item Participation in the PI's and Co-PI's bi-weekly research group
  meetings, in which members will be expected to present their research
  regularly, and feedback and coaching will be given to help all members
  to develop their communication and presentation skills.

\end{itemize}

Success of this mentoring plan will be assessed by tracking the progress
of the postdoctoral fellow through interviews of the postdoctoral fellow
to assess satisfaction with the mentoring program, and by tracking 
the postdoctoral fellow's progress toward his/her career goals after
finishing the postdoc.

\end{document}

